---
title: "Tags Pairs: Exploring R Questions' Tags on Stackoverflow"
date: "October 24, 2016"
output: 
html_document: 
keep_md: yes
toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE,message = FALSE,comment = " ")
```

# Overview

This script looks into **Stackoverflow's R-Questions** tags and explores relations. Questions are tagged with at least one tag, but the majority have more than one. For these questions, I will look into the occurance of pairs (e.g. ggplot2-histogram, or shiny-javascript,..etc.) and see the most frequent pairs. 

At the end, we will be able to make statements such as:

- **"shiny" appeared in x questions with "ggplot2"**  

- **"legend" is the 2nd most frequently mentioned tags with "ggplot2"**

- ...etc.

This could help identify the most frequently mentioned pairs of tags.

# Data Analysis

## Loading Libraries and Reading Data
```{r load library and read data}
# load libraries
library(tidyverse)
library(DT)

#read tags data
dat <- read.csv("../rquestions/Tags.csv",stringsAsFactors = FALSE)
```

## Exploring Dataset
```{r frequency of tags}
# count the frequency of each tag
datx <- dat %>%
        group_by(Tag) %>%
        summarise(N=n()) %>%
        arrange(desc(N))
```
We can see the frequency of each tag as follows:

```{r, echo=F}
datatable(datx)
```

## Tags Pairs

Here we will select the questions with **more than one tag** (in addition to R) and do the following:

- Step1: get all the tags corresponding to question ID
- Step2: find all  pair combinations from these tags
- Step3: combine all the pairs in one dataframe


### Step1 : get all the tags corresponding to question ID
```{r nest by Q_id}

# group by question ID and nest (for questions with more than one tag (+R))
datn <- dat %>% 
        group_by(Id) %>% 
        filter(n()>1) %>% 
        nest(.key="Tags")
```

Now if we lookk at a certain question ID, we find all the tags in one list:
```{r echo=F}
datn %>% 
        filter(Id==79709) %>% 
        .[["Tags"]]

```

```{r}
# and we can get them :
# datn$Tags[1]
```

### Step2: find all  pair combinations from these tags

Now, we will get all the possible pairs from the questions' tags:

```{r get tags pairs}
# map to function to get all the combinations from a list

datn <- datn %>% 
        mutate(pairs=map(Tags, ~combn(.x[["Tag"]], 2) %>% 
                                 t %>% 
                                 as.data.frame(stringsAsFactors = F)))
```

For the same row we checked in the previous step, we can see that the pairs are as follows:

```{r}
datn %>% 
        filter(Id==79709) %>% 
        .[["pairs"]]
```

### Step3: combine all the pairs in one dataframe

Now we will combine all the pairs for all questions, in one dataframe

```{r all pairs in one df}
dat_pairs <- plyr::rbind.fill(datn$pairs)

# put pairs in the same order
dat_pairs <- dat_pairs %>% 
        mutate(firstV=map2_chr(V1,V2,function(x,y) sort(c(x,y))[1]),
               secondV=map2_chr(V1,V2,function(x,y) sort(c(x,y))[2])
        ) %>% 
        select(-V1,-V2)

# count the frequency of each pair
pair_freq <- dat_pairs %>% 
        group_by(firstV,secondV) %>% 
        summarise(pair_count=n()) %>% 
        arrange(desc(pair_count)) %>% 
        ungroup()
```

Now we have the frequency of each pair as follows:

```{r}
datatable(pair_freq)
```

## Tag-Pairs for a Certain Tag

Here we can pick one tag and see all the other tags that appear with it and the frequency of each.

```{r GetTagPairs function}
# Get all pairs with a certain tag
GetTagPairs <- function(df, tag) {
        
         df %>% 
                filter(firstV==tag|secondV==tag) %>% 
                arrange(desc(pair_count)) %>% 
                mutate(T1 = ifelse(secondV==tag, secondV, firstV),
                       T2 = ifelse(secondV==tag, firstV, secondV)) %>% 
                select(T1, T2, pair_count)
}

```

### Example: ggplot2 Pairs

```{r}
ex <- GetTagPairs(pair_freq, "ggplot2")

datatable(ex)
```

```{r}
datx1 <- datx %>% 
        mutate(pairs = map(Tag, ~GetTagPairs(pair_freq,.x)))
```

